---
title: "An Evidence-based Forecast: Gold as a Traditional Safe-Haven Investment"
author: "Yuqiao Yang"

execute:
  echo: false
  
bibliography: references.bib
---

> **Abstract.** This research aims to explore future trends in Gold prices as a traditonal safe-haven investment using a Bayesian VARs model. In the wake of the 2008 financial crisis and especially the 2019 global Covid-19 pandemic, the world economy appears to be on the brink of a looming risk: a world-wide economic recession. The concern over the risk of investment returns has become a primary focus for global investors and financial institutions. This unease has been further exacerbated by geopolitical conflicts such as the Russia-Ukraine war(2022) and the Israeli-Palestinian conflict (2023). Consequently, this research aims to provide a briefly discussion and data-driven forecast of traditional safe-haven assets: Gold, under current circumstances. Factors considered include emerging safe-haven investments, risk-free investment assets, comparable investments, market returns, inflation on both demand and supply sides, broad money supply (M2), interest rates, unemployment rates and market volatility.
>
> **Keywords.** Bayesian VARs, Gold price, Inflation, Interset rate, Unemployments, US Bond Yeild, Safe-haven Assets, Forecasting, Volatility, R, Quarto.

# Introduction

**Objective:**

This research project aims to provide a monthly based, data-driven forecast of Gold price(USD) in two years, utilizing a Bayesian VARs model.

**Question:**

Gold as a traditional safe-haven asset, what are the anticipated price movements for the next year or beyond within the current environment?

**Introduction:**

Ulrich Beck introduced the concept of the risk society in the late 20th century, highlighting how humans confront entirely different systemic risks and face challenges in risk allocation under industrial society. Concurrently, globalization has reshaped the world and transformed human perceptions and experiences. Increasingly, evidence suggests that humanity is entering the risk society as described by Beck. Globalization encompasses not only economic, finance, technologe, and culture, but also risks. A China's financial exchange restriction might influence Australia's housing prices, while decisions made by the U.S. Central Bank regarding interest rates can prompt Western central banks to follow suit simultaneously. Following the 2008 financial crisis, major economies mitigated its aftermath significantly through quantitative easing monetary policies. This injection of substantial liquidity propelled economic growth steadily, leading to unprecedented prosperity in specific industries. However, the limitations of quantitative easing became apparent as the Covid-19 pandemic drew to a close. The United States and Western countries experienced unprecedented hyperinflation, coupled with indicators such as rising unemployment rates inversely correlated with inflation, conflicting long-term government bond yields with short-term treasuries, and record-breaking composite indices, signaling an impending global recession.

Geopolitical conflicts, such as the Russia-Ukraine war and the Israeli-Palestinian conflict, have intensified various risks. Disruptions in oil supply, blockages in key waterways, and logistical challenges in transporting goods and agricultural products have further exacerbated commodity price hikes and inflationary pressures. Consequently, mitigating or hedging investment risks has become the primary focus for global investors and financial institutions.

Among various safe-haven investments, gold has regained popularity as a hedge against uncertainty. This research aims to provide investors with a data-supported prediction of gold price trends over the next two years using Bayesian VAR models. The study incorporates information on comparable and emerging hedging products, market risks, returns, unemployment rates, inflation, interest rates, and other relevant parameters to construct a robust Bayesian VAR model. Ultimately, this research aids investors in identifying gold price trends and confidence intervals under different uncertainties within the current environment, thereby mitigating investment risks effectively.

# Data and Data Properties

To enhance the accuracy of gold price predictions, a total selection of 17 variables has been chosen, encompassing gold competitors, risk-free assets, gold futures, and the Nasdaq index. From a broader macroeconomic standpoint, the variables also include inflation, the Producer Price Index (PPI), unemployment rates, crude oil prices, volatility indices, the dollar index, changes in the M2 money supply level, and federal fund effective rates.

-   $GoldETF_{t}$: Gold current price in USD per 0.1 ounce, present by SPDR Gold Shares (GLD), which minus management fees.

-   Competitors and Substitutes for Gold ：

    -   $GoldFutures_{t}$ : Gold future price in USD per ounce, as considering the expectations in further gold price movements and high liquidity safe haven currency than real product.
    -   $BITUSD_{t}$ : As an emerging investment product, with the concept of decentralization, it has become a risk-averse investment product for many investors and financial institutions.
    -   Risk-free assets: treasury bonds
        -   $13WeekNotes_{t}$ : Considering as short-term risk free assets return. More time using in short term risk hedging in portfolio.
        -   $Tbill(5Year)_{t}$ : Considering as mid-term risk free assets return.
        -   $Tbill(10Year)_{t}$ : Considering as mid-term risk free assets return.
        -   $Tbill(30Year)_{t}$ : Considering as long-term risk free assets return.

-   Market returns as opposed to safe-haven investments：

    -   $NasdaqIndex_{t}$ ：Index that include all stocks available in NASDAQ to present the market returns.

-   Macro environment：

    -   $M2_{t}$ : the Board money supply of United States cause price index goes up.
    -   $Infla_{t}$ : CPI Index that present whole price level changes of all goods and services in US. Gold price are highly correlated with inflation.
    -   $Unemp_{t}$ : unemployment rate provide by Bureau of Statistic of US to present a general environment of Labor market.
    -   $CrudeOil_{t}$ : to present as basic cost of production.
    -   $PPI(industry)_{t}$ : to present production side inflation of increase in cost in percentage.
    -   $PPI(commodity)_{t}$ : to present production side inflation of increase in cost in percentage.
    -   $FFERs_{t}$ : As the Federal Funds Effective Rates aim to lower the inflation, decrease the M2 level.
    -   $USDIndex_{t}$ : to present as the purchasing power of USD cross world-wide. That increase the total amount of investors and financial institutions come into US market to earn higher returns.
    -   $VolatilityIndex_{t}$ : to present the risk cross whole market and expectations of further coming events.

```{r Library}
#| echo: false
#| message: false
#| warning: false

library(readabs)
library(fredr)
library(blscrapeR)
library(readrba)
library(xts)
library(fUnitRoots)   # ADF test - adfTest
library(tidyverse)    # for table
library(kableExtra)   # for print table
library(dplyr)
library(corrplot)
library(tseries) # for adf test
```

```{r}
#| echo: false
#| message: false
#| warning: false

# 1.Gold current price in USD per 0.1 ounce, present by SPDR Gold Shares (GLD)
goldETF_link = "https://query1.finance.yahoo.com/v7/finance/download/GLD?period1=1199232000&period2=1712016000&interval=1mo&events=history&includeAdjustedClose=true"
goldETF_download = read.csv(goldETF_link)
names(goldETF_download) <- tolower(names(goldETF_download))
gold_ETF_data <- goldETF_download %>%
  select("date","gold_ETF_data" = "adj.close")

# 2. Gold futures price in USD per ounce
gold_link = "https://query1.finance.yahoo.com/v7/finance/download/GC%3DF?period1=1009843200&period2=1703980800&interval=1mo&filter=history&frequency=1mo&includeAdjustedClose=true"
gold_download = read.csv(gold_link)
names(gold_download) <- tolower(names(gold_download))
gold_future_data <- gold_download %>%
  select("date","gold_future_data" = "adj.close")

# 3. BIT - USD
BIT_USD = "https://query1.finance.yahoo.com/v7/finance/download/BTC-USD?period1=1410912000&period2=1712102400&interval=1mo&events=history&includeAdjustedClose=true"
BIT_USD_file = read.csv(BIT_USD)
names(BIT_USD_file) <- tolower(names(BIT_USD_file))
BIT_USD_data <- BIT_USD_file %>%
  select("date","BIT_USD_data" = "adj.close")

# 4. 13 Weeks treasury bond yield
bond_yield_13weeks = "https://query1.finance.yahoo.com/v7/finance/download/%5EIRX?period1=-315360000&period2=1712102400&interval=1mo&events=history&includeAdjustedClose=true"
bond_yield_13weeks_file = read.csv(bond_yield_13weeks)
names(bond_yield_13weeks_file) <- tolower(names(bond_yield_13weeks_file))
bond_yield_13weeks_data <- bond_yield_13weeks_file %>%
  select("date","bond_yield_13weeks_data" = "adj.close")

# 5. 5-Year treasury bond yield
bond_yield_5years = "https://query1.finance.yahoo.com/v7/finance/download/%5EFVX?period1=-252374400&period2=1712016000&interval=1mo&events=history&includeAdjustedClose=true"
bond_yield_5years_file = read.csv(bond_yield_5years)
names(bond_yield_5years_file) <- tolower(names(bond_yield_5years_file))
bond_yield_5years_data <- bond_yield_5years_file %>%
  select("date","bond_yield_5years_data" = "adj.close")

# 6. 10-Year treasury bond yield
bond_yield_10years = "https://query1.finance.yahoo.com/v7/finance/download/%5ETNX?period1=-252374400&period2=1712016000&interval=1mo&events=history&includeAdjustedClose=true"
bond_yield_10_years = read.csv(bond_yield_10years)
names(bond_yield_10_years) <- tolower(names(bond_yield_10_years))
bond_yield_10_years_data <- bond_yield_10_years %>%
  select("date","bond_yield_10_years_data" = "adj.close")

# 7. 30-Year treasury bond yield
bond_yield_30years = "https://query1.finance.yahoo.com/v7/finance/download/%5ETYX?period1=224812800&period2=1712102400&interval=1mo&events=history&includeAdjustedClose=true"
bond_yield_30years_file = read.csv(bond_yield_30years)
names(bond_yield_30years_file) <- tolower(names(bond_yield_30years_file))
bond_yield_30years_data <- bond_yield_30years_file %>%
  select("date","bond_yield_30years_data" = "adj.close")

# 8. Nasdaq Index
Nasdaq_IXIC = "https://query1.finance.yahoo.com/v7/finance/download/%5EIXIC?period1=34646400&period2=1712102400&interval=1mo&events=history&includeAdjustedClose=true"
Nasdaq_IXIC_file = read.csv(Nasdaq_IXIC)
names(Nasdaq_IXIC_file) <- tolower(names(Nasdaq_IXIC_file))
Nasdaq_IXIC_data <- Nasdaq_IXIC_file %>%
  select("date","Nasdaq_IXIC_data" = "adj.close")

# 9. M2 level
M2_rate = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=WM2NS&scale=left&cosd=1980-11-03&coed=2024-03-04&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=eop&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=pch&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1980-11-03"
M2_rate_file = read.csv(M2_rate)
names(M2_rate_file) <- tolower(names(M2_rate_file))
M2_rate_data <- M2_rate_file %>%
  select("date","M2_rate_data" = "wm2ns_pch")

# 10. Inflation rate
Inflation_rate = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=CPIAUCSL&scale=left&cosd=1947-01-01&coed=2024-02-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=eop&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=pch&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1947-01-01"
Inflation_rate_file = read.csv(Inflation_rate)
names(Inflation_rate_file) <- tolower(names(Inflation_rate_file))
Inflation_rate_data <- Inflation_rate_file %>%
  select("date","Inflation_rate_data" = "cpiaucsl_pch")

# 11. Unemployment rate
unemployment_rate = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=UNRATE&scale=left&cosd=1948-01-01&coed=2024-02-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2024-04-02&revision_date=2024-04-02&nd=1948-01-01"
unemployment_rate_file = read.csv(unemployment_rate)
names(unemployment_rate_file) <- tolower(names(unemployment_rate_file))
unemployment_rate_data <- unemployment_rate_file %>%
  select("date","unemployment_rate_data" = "unrate")

# 12. Crude oil price
Crude_oil_price = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=off&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=DCOILBRENTEU&scale=left&cosd=1990-01-01&coed=2024-03-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=eop&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1987-05-20"
Crude_oil_price_file = read.csv(Crude_oil_price)
names(Crude_oil_price_file) <- tolower(names(Crude_oil_price_file))
Crude_oil_price_data <- Crude_oil_price_file %>%
  select("date","Crude_oil_price_data" = "dcoilbrenteu")

# 13. PPI - Industry
PPI_industry_rate = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=PCUOMFGOMFG&scale=left&cosd=1984-12-01&coed=2024-02-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=pch&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1984-12-01"
PPI_industry_rate_file = read.csv(PPI_industry_rate)
names(PPI_industry_rate_file) <- tolower(names(PPI_industry_rate_file))
PPI_industry_rate_data <- PPI_industry_rate_file %>%
  select("date","PPI_industry_rate_data" = "pcuomfgomfg_pch")

# 14. PPI - Commodity
PPI_commodity_rate = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=PPIACO&scale=left&cosd=1913-01-01&coed=2024-02-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=pch&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1913-01-01"
PPI_commodity_rate_file = read.csv(PPI_commodity_rate)
names(PPI_commodity_rate_file) <- tolower(names(PPI_commodity_rate_file))
PPI_commodity_rate_data <- PPI_commodity_rate_file %>%
  select("date","PPI_commodity_rate_data" = "ppiaco_pch")

# 15. Federal Funds Effective Rates
Federal_funds_rate = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=FEDFUNDS&scale=left&cosd=1990-01-01&coed=2024-03-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1954-07-01"
Federal_funds_rate_file = read.csv(Federal_funds_rate)
names(Federal_funds_rate_file) <- tolower(names(Federal_funds_rate_file))
Federal_funds_rate_data <- Federal_funds_rate_file %>%
  select("date","Federal_funds_rate_data" = "fedfunds")

# 16. US dollars Index
US_dollars_Index = "https://query1.finance.yahoo.com/v7/finance/download/DX-Y.NYB?period1=31795200&period2=1712102400&interval=1mo&events=history&includeAdjustedClose=true"
US_dollars_Index_file = read.csv(US_dollars_Index)
names(US_dollars_Index_file) <- tolower(names(US_dollars_Index_file))
US_dollars_Index_data <- US_dollars_Index_file %>%
  select("date","US_dollars_Index_data" = "adj.close")

# 17. Volatility Index
Volatility_Index = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=VIXCLS&scale=left&cosd=1990-01-02&coed=2024-03-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=eop&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1990-01-02"
Volatility_Index_file = read.csv(Volatility_Index)
names(Volatility_Index_file) <- tolower(names(Volatility_Index_file))
Volatility_Index_data <- Volatility_Index_file %>%
  select("date","Volatility_Index_data" = "vixcls")

```


```{r}
#| echo: false
#| message: false
#| warning: false
data_list <-    list(gold_ETF_data,           gold_future_data, 
                     BIT_USD_data,            bond_yield_13weeks_data, 
                     bond_yield_5years_data,  bond_yield_10_years_data,  
                     bond_yield_30years_data, Nasdaq_IXIC_data, 
                     M2_rate_data,            Inflation_rate_data,
                     unemployment_rate_data,  Crude_oil_price_data,
                     PPI_industry_rate_data,  PPI_commodity_rate_data,
                     Federal_funds_rate_data, US_dollars_Index_data,
                     Volatility_Index_data)  


merged_data <- Reduce(function(x, y) merge(x, y, by = "date", all = TRUE), data_list)


start_date <- as.Date("2014-01-01")
end_date <- as.Date("2024-04-01")
filtered_data <- merged_data %>%
  filter(date >= start_date & date <= end_date)

filtered_data <- na.omit(filtered_data)

```

After download all variables as designed, merge all data sets into a new frame and change the column names. The date of data used in this research will start at 2014-10-01 as at 2024-04-01.

# Plots of all variables

```{r}
#| echo: false
#| message: false
#| warning: false

data1 <- subset(filtered_data, select = -c(date))

data1 <- mutate_all(data1, as.numeric)

par(mfrow = c(4, 4), mar=c(2,2,2,2))
for (i in 1:17) { 
  ts.plot(data1[, i], main = colnames(data1)[i], 
          ylab = "", xlab = "")
}


```

As above, we could have all 17 variables in visualization format individually. As a quick overlook, 13 weeks bond has a similar trend with federal funds effective rates; other 3 treasury bonds move quite same; gold and its' future, Nasdaq, Bit coin, crude oil price and US dollars Index have upper ward trends; Unemployment rates seems like opposite to federal rates; M2 and other 3 time series seems like stationary on mean but variance change over time.

**Correlation Table**

```{r}
#| echo: false
#| message: false
#| warning: false

correlation_matrix <- cor(data1)

corrplot(correlation_matrix, method = "color", type = "upper", tl.srt = 45,tl.col = "black",tl.cex = 0.5)
```
A simple correlation provide us a basic understanding of those 17 variables. Gold as safe-haven is highly positive correlated with Gold future and Nasdaq Index. Seems like its also a strong bond between Bit coin and Gold, however other factors not shown as strong correlation with Gold price.

Therefore, we could use ACF and PACF test to indicate whether there is autocorrelations.

```{r}
#| echo: false
#| message: false
#| warning: false

par(mfrow = c(4, 4), mar=c(2,2,2,2))
for (i in 1:17){
acf = acf(data1[,i], plot = FALSE)[1:20]
plot(acf, main = "")
title(main = paste(colnames(data1)[i]), line = 0.5)
}

par(mfrow = c(4, 4), mar=c(2,2,2,2))
for (i in 1:17){
pacf = pacf(data1[,i], plot = FALSE)[1:20]
plot(pacf, main = "")
title(main = paste(colnames(data1)[i]), line = 0.5)
}
```

Both ACF and PACF suggest that variables are highly autocorrelated except M2: Board money change rate. That might because the policy has changed in earlier 2020 and 2022. Therefore, we further need ADF test(unit root test) to feed our time series are stationary or not.

```{r}
#| echo: false
#| message: false
#| warning: false

adf_test <- list()
for (i in 1:17) {
  adf_result = adf.test(data1[,i], k = 4)
  adf_test[[i]] <- adf_result
}
adf_table <- data.frame(p_value = numeric(length(adf_test)))
adf_table <- data.frame(p_value = numeric(length(adf_test)))
for (i in 1:length(adf_test)) {adf_table[i, "p_value"] = round(adf_test[[i]]$p.value,3)
}

rownames(adf_table)<- c("gold_ETF_data",           "gold_future_data", 
                     "BIT_USD_data",            "bond_yield_13weeks_data", 
                     "bond_yield_5years_data",  "bond_yield_10_years_data",  
                     "bond_yield_30years_data", "Nasdaq_IXIC_data", 
                     "M2_rate_data",            "Inflation_rate_data",
                    "unemployment_rate_data",  "Crude_oil_price_data",
                     "PPI_industry_rate_data",  "PPI_commodity_rate_data",
                     "Federal_funds_rate_data", "US_dollars_Index_data",
                     "Volatility_Index_data")
colnames(adf_table)<- c("P-value")
print(adf_table)
```


# Model and Hypothesis

This research project based on **Bayesian VARs(p) model** to forecast the Gold price in next two years. For time $t$ = {1,2,3,...,$T-1$,$T$} :

```{=tex}
\begin{aligned}
y_t &= \mu_0 + A_1y_{t-1} + A_2y_{t-2}...+A_py_{t-p} +\epsilon_t\\

\epsilon_t|Y_{t-1} &\sim iid \mathcal{N}_{17}(0_{17}, \Sigma)
\end{aligned}
```
Where N = 17 and $y_{t}$ is a vector of 17 variables at time $t$.

```{=tex}
\begin{aligned}

y_{t}=\begin{pmatrix}
GoldETF_{t} \\
GoldFutures_{t}\\
BITUSD_{t} \\
13WeekNotes_{t}\\
Treasurybill(5Year)_{t} \\
Treasurybill(10Year)_{t} \\
Treasurybill(30Year)_{t} \\
NasdaqIndex_{t} \\
M2_{t} \\
Inflation_{t} \\
Unemployment_{t}\\
CrudeOil_{t}\\
PPI(industry)_{t} \\
PPI(commodity)_{t}\\
FFERs_{t} \\
USDollarIndex_{t}\\
VolatilityIndex_{t}\\

\end{pmatrix}

\end{aligned}
```
For time $t$ = 1,2,.....,$T$：

-   $y_t$ is a $N(17)\times 1$ vector of observations at time $t$
-   $\mu_0$ is a $N(17)\times 1$ vector of constant terms
-   $A_i$ is a $N(17)\times N(17)$ matrix of autoregressive slope parameters
-   $\epsilon_t$ is a $N(17)\times 1$ vector of error terms which is a multivariate white nose process(time invariant)
-   $Y_{t-1}$ is the information set collecting observations on y up to time $t-1$
-   $\Sigma$ is a $N(17)\times N(17)$ covariance matrix of the error term

Base on the model above, we could first turn B Vars(p) model into B Vars(1) model and easily regress to have the parameter matrix. Then we could have a $t+h$ period forward forecasting with increase of variance, in this case: $h$ = 24.

The main focus of estimate output is the conditional mean of Gold price, which base on current information set $Y_{t-1}$. It provide the average mean prediction of Gold price which investors and financial institutions interested in. Moreover, 1 standard deviation and 2 standard deviation will also produced in forecasting process to provide a 68% and 95% of confidence intervals of future Gold price movements in $h$ periods base on current information set.

Furthermore, different prior distribution might be used to provide different level of uncertainty of current environment(information set). Compare the difference of Gold price under different priors could help to prove the Gold as a high quality safe-haven investment and increase investors and financial institutions confidence and further expectations. ( Competitors for golds might also be used under different priors, such as BIT-USD, Nasdaq Index and short to mid-term treasury bills. )

## References {.unnumbered}
