---
title: "An Evidence-based Forecast: Gold as a Traditional Safe-Haven Investment"
author: "Yuqiao Yang"

execute:
  echo: false
  
bibliography: references.bib
---

> **Abstract.** This research aims to explore future trends in Gold prices as a traditonal safe-haven investment using a Bayesian VARs model. In the wake of the 2008 financial crisis and especially the 2019 global Covid-19 pandemic, the world economy appears to be on the brink of a looming risk: a world-wide economic recession. The concern over the risk of investment returns has become a primary focus for global investors and financial institutions. This unease has been further exacerbated by geopolitical conflicts such as the Russia-Ukraine war(2022) and the Israeli-Palestinian conflict (2023). Consequently, this research aims to provide a briefly discussion and data-driven forecast of traditional safe-haven assets: Gold, under current circumstances. Factors considered include emerging safe-haven investments, risk-free investment assets, comparable investments, market returns, inflation on both demand and supply sides, broad money supply (M2), interest rates, unemployment rates and market volatility. 
>
> **Keywords.** Bayesian VARs, Gold price, Inflation, Interset rate, Unemployments, US Bond Yeild, Safe-haven Assets, Forecasting, Volatility, R, Quarto.

# Introduction

**Objective:**

This research project aims to provide a monthly based, data-driven forecast of Gold price(USD) in two years, utilizing a Bayesian VARs model.

**Question:**

Gold as a traditional safe-haven asset, what are the anticipated price movements for the next year or beyond within the current environment?

**Introduction:**

Ulrich Beck introduced the concept of the risk society in the late 20th century, highlighting how humans confront entirely different systemic risks and face challenges in risk allocation under industrial society. Concurrently, globalization has reshaped the world and transformed human perceptions and experiences. Increasingly, evidence suggests that humanity is entering the risk society as described by Beck. Globalization encompasses not only economic, finance, technologe, and culture, but also risks. A China's financial exchange restriction might influence Australia's housing prices, while decisions made by the U.S. Central Bank regarding interest rates can prompt Western central banks to follow suit simultaneously. Following the 2008 financial crisis, major economies mitigated its aftermath significantly through quantitative easing monetary policies. This injection of substantial liquidity propelled economic growth steadily, leading to unprecedented prosperity in specific industries. However, the limitations of quantitative easing became apparent as the Covid-19 pandemic drew to a close. The United States and Western countries experienced unprecedented hyperinflation, coupled with indicators such as rising unemployment rates inversely correlated with inflation, conflicting long-term government bond yields with short-term treasuries, and record-breaking composite indices, signaling an impending global recession.

Geopolitical conflicts, such as the Russia-Ukraine war and the Israeli-Palestinian conflict, have intensified various risks. Disruptions in oil supply, blockages in key waterways, and logistical challenges in transporting goods and agricultural products have further exacerbated commodity price hikes and inflationary pressures. Consequently, mitigating or hedging investment risks has become the primary focus for global investors and financial institutions.

Among various safe-haven investments, gold has regained popularity as a hedge against uncertainty. This research aims to provide investors with a data-supported prediction of gold price trends over the next two years using Bayesian VAR models. The study incorporates information on comparable and emerging hedging products, market risks, returns, unemployment rates, inflation, interest rates, and other relevant parameters to construct a robust Bayesian VAR model. Ultimately, this research aids investors in identifying gold price trends and confidence intervals under different uncertainties within the current environment, thereby mitigating investment risks effectively.

# Data and Data Properties

To enhance the accuracy of gold price predictions, a total selection of 17 variables has been chosen, encompassing gold competitors, risk-free assets, gold futures, and the Nasdaq index. From a broader macroeconomic standpoint, the variables also include inflation, the Producer Price Index (PPI), unemployment rates, crude oil prices, volatility indices, the dollar index, changes in the M2 money supply level, and federal fund effective rates.

 * $GoldETF_{t}$: Gold current price in USD per 0.1 ounce, present by SPDR Gold Shares (GLD), which minus management fees.
 * Competitors and Substitutes for Gold ：
   + $GoldFutures_{t}$ : Gold future price in USD per ounce, as considering the expectations in further gold price movements and high liquidity safe haven currency than real product.
   + $BITUSD_{t}$ : As an emerging investment product, with the concept of decentralization, it has become a risk-averse investment product for many investors and financial institutions. 
   + Risk-free assets: treasury bonds
     - $13WeekNotes_{t}$ : Considering as short-term risk free assets return. More time using in short term risk hedging in portfolio.
     - $Treasurybill(5Year)_{t}$ : Considering as mid-term risk free assets return.
     - $Treasurybill(10Year)_{t}$ : Considering as mid-term risk free assets return.
     - $Treasurybill(30Year)_{t}$ : Considering as long-term risk free assets return. 
 * Market returns as opposed to safe-haven investments：
   + $NasdaqIndex_{t}$ ：Index that include all stocks available in NASDAQ to present the market returns. 
 * Macro environment
   + $M2_{t}$ : the Board money supply of United States cause price index goes up.
   + $Inflation_{t}$ : CPI Index that present whole price level changes of all goods and services in US. Gold price are highly correlated with inflation.
   + $Unemployment_{t}$ : unemployment rate provide by Bureau of Statistic of US to present a general environment of Labor market.
   + $CrudeOil_{t}$ : to present as basic cost of production.
   + $PPI(industry)_{t}$ : to present production side inflation of increase in cost in percentage.
   + $PPI(commodity)_{t}$ : to present production side inflation of increase in cost in percentage.
   + $FFERs_{t}$ : As the Federal Funds Effective Rates aim to lower the inflation, decrease the M2 level.
   + $USDollarIndex_{t}$ : to present as the purchasing power of USD cross world-wide. That increase the total amount of investors and financial institutions come into US market to earn higher returns.
   + $VolatilityIndex_{t}$ : to present the risk cross whole market and expectations of further coming events.
   
 
```{r Library}
#| echo: false
#| message: false
#| warning: false

library(readabs)
library(fredr)
library(blscrapeR)
library(readrba)
library(xts)
library(fUnitRoots)   # ADF test - adfTest
library(tidyverse)    # for table
library(kableExtra)   # for print table
```


```{r}
#| echo: false
#| message: false
#| warning: false

# 1.Gold currentprice in USD per 0.1 ounce, present by SPDR Gold Shares (GLD)
goldETF_link = "https://query1.finance.yahoo.com/v7/finance/download/GLD?period1=1199232000&period2=1712016000&interval=1mo&events=history&includeAdjustedClose=true"
goldETF_download = read.csv(goldETF_link)
gold_ETF_data = goldETF_download[,6]
plot.ts(gold_ETF_data)

# 2. Gold futures price in USD per ounce
gold_link = "https://query1.finance.yahoo.com/v7/finance/download/GC%3DF?period1=1009843200&period2=1703980800&interval=1mo&filter=history&frequency=1mo&includeAdjustedClose=true"
gold_download = read.csv(gold_link)
gold_furture_data = gold_download[,6]
plot.ts(gold_furture_data)

# 3. BIT - USD
BIT_USD = "https://query1.finance.yahoo.com/v7/finance/download/BTC-USD?period1=1410912000&period2=1712102400&interval=1mo&events=history&includeAdjustedClose=true"
BIT_USD_file = read.csv(BIT_USD)
head(BIT_USD_file)
BIT_USD_data = BIT_USD_file[,2]
plot.ts(BIT_USD_data)

# 4. 13 Weeks treasury bond yield
bond_yield_13weeks = "https://query1.finance.yahoo.com/v7/finance/download/%5EIRX?period1=-315360000&period2=1712102400&interval=1mo&events=history&includeAdjustedClose=true"
bond_yield_13weeks_file = read.csv(bond_yield_13weeks)
head(bond_yield_13weeks_file)
bond_yield_13weeks_data = bond_yield_13weeks_file[,2]
plot.ts(bond_yield_13weeks_data)

# 5. 5-Year treasury bond yield
bond_yield_5years = "https://query1.finance.yahoo.com/v7/finance/download/%5EFVX?period1=-252374400&period2=1712016000&interval=1mo&events=history&includeAdjustedClose=true"
bond_yield_5years_file = read.csv(bond_yield_5years)
head(bond_yield_5years_file)
bond_yield_5years_data = bond_yield_5years_file[,2]
plot.ts(bond_yield_5years_data)

# 6. 10-Year treasury bond yield
bond_yield_10years = "https://query1.finance.yahoo.com/v7/finance/download/%5ETNX?period1=-252374400&period2=1712016000&interval=1mo&events=history&includeAdjustedClose=true"
bond_yield_10_years = read.csv(bond_yield_10years)
bond_yield_10_years_data = bond_yield_10_years[,6]
plot.ts(bond_yield_10_years_data)

# 7. 30-Year treasury bond yield
bond_yield_30years = "https://query1.finance.yahoo.com/v7/finance/download/%5ETYX?period1=224812800&period2=1712102400&interval=1mo&events=history&includeAdjustedClose=true"
bond_yield_30years_file = read.csv(bond_yield_30years)
head(bond_yield_30years_file)
bond_yield_30years_data = bond_yield_30years_file[,2]
plot.ts(bond_yield_30years_data)

# 8. Nasdaq Index
Nasdaq_IXIC = "https://query1.finance.yahoo.com/v7/finance/download/%5EIXIC?period1=34646400&period2=1712102400&interval=1mo&events=history&includeAdjustedClose=true"
Nasdaq_IXIC_file = read.csv(Nasdaq_IXIC)
head(Nasdaq_IXIC_file)
Nasdaq_IXIC_data = Nasdaq_IXIC_file[,2]
plot.ts(Nasdaq_IXIC_data)

# 9. M2 level
M2_rate = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=WM2NS&scale=left&cosd=1980-11-03&coed=2024-03-04&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=eop&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=pch&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1980-11-03"
M2_rate_file = read.csv(M2_rate)
head(M2_rate_file)
M2_rate_data = M2_rate_file[,2]
plot.ts(M2_rate_data)

# 10. Inflation rate
Inflation_rate = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=CPIAUCSL&scale=left&cosd=1947-01-01&coed=2024-02-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=eop&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=pch&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1947-01-01"
Inflation_rate_file = read.csv(Inflation_rate)
head(Inflation_rate_file)
Inflation_rate_data = Inflation_rate_file[,2]
plot.ts(Inflation_rate_data)

# 11. Unemployment rate
unemployment_rate = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=UNRATE&scale=left&cosd=1948-01-01&coed=2024-02-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2024-04-02&revision_date=2024-04-02&nd=1948-01-01"
unemployment_rate_file = read.csv(unemployment_rate)
unemployment_rate_data = unemployment_rate_file[,2]
plot.ts(unemployment_rate_data)

# 12. Crude oil price
Crude_oil_price = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=off&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=DCOILBRENTEU&scale=left&cosd=1990-01-01&coed=2024-03-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=eop&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1987-05-20"
Crude_oil_price_file = read.csv(Crude_oil_price)
head(Crude_oil_price_file)
Crude_oil_price_data = Crude_oil_price_file[,2]
plot.ts(Crude_oil_price_data)

# 13. PPI - Industry
PPI_industry_rate = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=PCUOMFGOMFG&scale=left&cosd=1984-12-01&coed=2024-02-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=pch&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1984-12-01"
PPI_industry_rate_file = read.csv(PPI_industry_rate)
head(PPI_industry_rate_file)
PPI_industry_rate_data = PPI_industry_rate_file[,2]
plot.ts(PPI_industry_rate_data)

# 14. PPI - Commondity
PPI_commodity_rate = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=WM2NS&scale=left&cosd=1980-11-03&coed=2024-03-04&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=eop&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=pch&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1980-11-03"
PPI_commodity_rate_file = read.csv(PPI_commodity_rate)
head(PPI_commodity_rate_file)
PPI_commodity_rate_data = PPI_commodity_rate_file[,2]
plot.ts(PPI_commodity_rate_data)

# 15. Federal Funds Effective Rates
Federal_funds_rate = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=FEDFUNDS&scale=left&cosd=1990-01-01&coed=2024-03-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1954-07-01"
Federal_funds_rate_file = read.csv(Federal_funds_rate)
head(Federal_funds_rate_file)
Federal_funds_rate_data = Federal_funds_rate_file[,2]
plot.ts(Federal_funds_rate_data)

# 16. US dollars Index
US_dollars_Index = "https://query1.finance.yahoo.com/v7/finance/download/DX-Y.NYB?period1=31795200&period2=1712102400&interval=1mo&events=history&includeAdjustedClose=true"
US_dollars_Index_file = read.csv(US_dollars_Index)
head(US_dollars_Index_file)
US_dollars_Index_data = US_dollars_Index_file[,2]
plot.ts(US_dollars_Index_data)

# 17. Volatility Index
Volatility_Index = "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1318&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=VIXCLS&scale=left&cosd=1990-01-02&coed=2024-03-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=eop&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2024-04-03&revision_date=2024-04-03&nd=1990-01-02"
Volatility_Index_file = read.csv(Volatility_Index)
head(Volatility_Index_file)
Volatility_Index_data = Volatility_Index_file[,2]
plot.ts(Volatility_Index_data)

```



# Model and Hypothesis

This research project based on **Bayesian VARs(p) model** to forecast the Gold price in next two years. For $$\text{t} = {1,2,3,...,T-1,T}$$ :

$$y_t &= \mu_0 + A_1y_{t-1} + A_2y_{t-2}...+A_py_{t-p} +\epsilon_t\\

\epsilon_t|y_{t-1} &\sim iid \mathcal{N}_{17}(0_{17}, \Sigma)$$

**In Matrix notation**
$$
Y &= XA+E\\
E|X &\sim \mathcal{MN}_{T\times 17}(0,\Sigma,I_T)
$$


## References {.unnumbered}